\papertitle

### 2012-10-13 manuscript.tex
Recompress pf_screencap
Reworking introduction. Draft.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\begin{figure}[!tb]
\centering
\includegraphics[width=\linewidth]{figures/h2bird.png}
\caption{H$^2$Bird ornithopter MAV}
\label{fig:h2bird}
\end{figure}
The power, size, and weight constraints of micro air vehicle (MAV) 
platforms significantly limit on-board sensing and computational 
resources, and thus the complexity of the control and state estimation 
algorithms which can be executed on-board. These constraints are 
particularly severe for flapping wing MAVs, a class of MAVs that have inherently superior 
safety, and noise profile to rotor craft MAVs, but at the 
expense of payload weight.
%Intro portion about previous works in ornithopter coorperative control/
%modeling ( won't necessarily stay in this spot)
Modeling and control of flapping wing MAVs is becoming a well studied subject\cite{floreano:flying}. 
Shigeoka discusses velocity and altitude control in ~\cite{Shigeoka:ornithopter}. 
Design and control of the sub-15 gram DelFly ornithopter is described by 
deCroon et al.~\cite{delfly:design}. In contrast, there is little previous work 
on guidance of flapping wing MAVs. Baek demonstrated altitude control with an external 
camera~\cite{baek:altitude}. de Croon et al. demonstrated obstacle avoidance 
with an onboard camera and offboard processing~\cite{delfly:avoid}. For sub-20 gram
ornithopters, Baek et al. \cite{baek:tracking} is one of the few examples of
completely autonomous target seeking.
%[However, these papers do not study the system blah blah blah.]

Autonomous control of flapping winged MAVs is a complex undertaking because of
the non-linear flight dynamics~\cite{humbert:dipteran2}\cite{cheng:tandrdamping}. 
One approach to simplify these dynamic models is to use averaging over the wingbeat
period~\cite{Schenato:flightcontrol}\cite{cheng:tandrdamping}. We desire a
simpler approach, so we develop a linear, one-dimensional model to predict the
yaw behavior of the system, similar to the model that Shigeoka used
in~\cite{Shigeoka:ornithopter} for simulating the velocity of a MAV in
one-dimensionally. In addition to the nonlinearities, the system is
underactuated (there is no roll control) due to size constraints.

Many of the methods for controlling these platforms make extensive use of GPS in outdoor
environments and expansive motion capture systems in indoor environments
~\cite{kingston:timeattitude}\cite{kanade:3dvision}. While operating indoors, using
GPS to estimate the pose of the MAV is not possible, and motion capture
requires expensive and stationary modification of the environment. The power
and payload limits on MAVs make on-board sensing difficult, so multi-agent
cooperative control schemes are apt solutions.

@@

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\begin{figure}[!tb]
\centering
\includegraphics[width=\linewidth]{figures/h2bird.png}
\caption{H$^2$Bird ornithopter MAV}
\label{fig:h2bird}
\end{figure}
Power, size, and weight constraints for micro air vehicle (MAV) 
platforms are amongst the most restrictive of all robotic platforms. With
significantly limited sensing and computing capabilities, only the most rudimentary
control and state estimation algorithms can be executed on-board these platforms. 
Even more restrictive are the constraints for flapping wing MAVs, 
a class of MAVs that exhibit demonstrate safety and noise profiles superior to those
of rotor craft MAVs, but at the expense of reduced payload weight.

Compounding these engineering restrictions are the many non-linear
flight dynamics exhibited by flapping wing flight~\cite{humbert:dipteran2}\cite{cheng:tandrdamping}. 
Much past research on flapping wing MAVs has been focused on overcoming the 
difficulties associated with controlling and modeling in the face of these 
non-linearities\cite{floreano:flying}. Common approaches to simplify these 
dynamic models include averaging over the wingbeat period~\cite{Schenato:flightcontrol}
\cite{cheng:tandrdamping}, and using linear, low-dimensional models to predict the 
behavior in flight~\cite{Shigeoka:ornithopter}. Advances have lead to the
development of some high-performance platforms, such as the sub-15 gram DelFly 
as described by deCroon et al.~\cite{delfly:design}.

@@

In contrast, there is considerably less previous work on guidance of flapping wing MAVs. 
Baek demonstrated altitude control with an external camera~\cite{baek:altitude}. 
de Croon et al. demonstrated obstacle avoidance with an onboard camera and offboard 
processing~\cite{delfly:avoid}. For sub-20 gram ornithopters, Baek et al. 
\cite{baek:tracking} is one of the few examples of scompletely autonomous target seeking.

There also exists a body of work on guidance and control for fixed wing and rotary wing 
MAV platforms, but many of these methods make extensive use of GPS or motion capture systems
~\cite{kingston:timeattitude}\cite{kanade:3dvision}. While operating indoors, using
GPS to estimate the pose of the MAV is not possible, and motion capture
requires expensive and stationary modification of the environment. The power
and payload limits on flapping wing MAVs make on-board sensing difficult, so multi-agent
cooperative control schemes are apt solutions.

@@

%TODO Add in final paragraph to lead-in to our work
